Externalizing Worker Qualifications

### 2016-12-05 drafts/labor/abstract.tex
proposal (why didn't i put this up sooner?)

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{complexity}
\externaldocument{relationships}
\externaldocument{decomposition}
}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\onlyinsubfile{\plaintitle}
\begin{abstract}
The internet is enabling the rise of
crowd work,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has attempted to predict
the socio--technical outcomes of this shift, especially along three threads: %. This question has been dominated by three threads:
\begin{inlinelist}
\item \nameref{sec:complexity}?,
\item \nameref{sec:decomposition}?, and
\item \nameref{sec:relationships}?
\end{inlinelist}
In this paper, we look to the historical scholarship on piecework
--- a similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern crowd work.
We identify the mechanisms that enabled and limited piecework historically, and
identify whether crowd work faces the same pitfalls or might differentiate itself.
This approach introduces theoretical grounding that can help address
some of the most pernicious questions in crowd work,
and suggests design interventions that learn from history
rather than repeat it.
\end{abstract}
\end{document}

>>>>

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
  \externaldocument{complexity}
  \externaldocument{relationships}
  \externaldocument{decomposition}
}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\onlyinsubfile{\plaintitle}
\begin{abstract}
The internet is enabling the rise of
crowd work,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has attempted to predict
the socio--technical outcomes of this shift, especially along three threads:
\begin{inlinelist}
\item \nameref{sec:complexity}?,
\item \nameref{sec:decomposition}?, and
\item \nameref{sec:relationships}?
\end{inlinelist}
In this paper, we look to the historical scholarship on piecework
--- a similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern crowd work.
We identify the mechanisms that enabled and limited piecework historically, and
identify whether crowd work faces the same pitfalls or might differentiate itself.
This approach introduces theoretical grounding that can help address
some of the most pernicious questions in crowd work,
and suggests design interventions that learn from history
rather than repeat it.
\end{abstract}
\end{document}

### 2016-12-05 drafts/labor/cases.tex
proposal (why didn't i put this up sooner?)

\msb{this needs a transition into it. Before you lay out our method, lay out what we're trying to do. What's our goal here? THEN the method can explain how we achieved it. This might involve switching the order of some of the text here}

We look at lots of papers that use the term ``crowdsourcing'' or ``crowd work''
in the abstracts and titles of their papers,  especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework,  and how that affects the predictions and conclusions made in the piecework literature.

%\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,    overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:complexity},    \item \nameref{sec:decomposition}, and
  \item \nameref{sec:relationships}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,  discussing the extents to which work can be
decomposed,  contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
\msb{Our goal will be to use that literature to inform answers to the questions about crowd work (or something like that)}
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\subsubsection{So how does this affect crowd work?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}

% so CW?
% mechanism/limitation in pw?
% differences in cw? tech/access to intelligence?
% predicted outcome then? -> decompose effort/expertise access
% possible quirks/diffs?

% what can be decomposed? what can be evaluated?
% technology/turuing completeness gets us a win
% predefined expertise? you can find someone almost instantly;
% ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% huddler paper cites some decomposition stuff workflows are good/bad at things
% 3-way slack w/msb and mav
% academy of management 
% van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper
}

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  % \clearpage
  \nobalance{}
  }
  % \begin{appendices}
% \section{Graveyard}
\endnotetext{
\section{Cases notes}
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,      particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
  % }
  % \endnotetext{
  \subsection{What forms of work design and worker management are viable?}
  \begin{itemize}
    \item researchers have looked at how to increase worker productivity
    (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
    \cite{measuringCrowdsourcingCheng}.
    \item we've also seen people ``embrace error''
    \cite{embracingErrorKrishna}.
    \item still other research has looked into ways to sandbox workers from the context of their work 
    \item but scholarship looking into the design and management of work and workers isn't new;
    lots of research into getting pieceworkers to do work more quickly
    \cite{seymour1954manual}.
    \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
    (echoing similar research on Wikipedia and Mechanical Turk)
    \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
  \end{itemize}

>>>>

\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,    overcoming them through novel designs of work--flows and processes, and
  repeating the process~\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:complexity},
  \item \nameref{sec:decomposition}, and
  \item \nameref{sec:relationships}.
\end{inlinelist}
We'll explore these aspects of crowdsourcing,  discussing the extents to which work can be
decomposed,  contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
\msb{Our goal will be to use that literature to inform answers to the questions about crowd work (or something like that)}
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\subsubsection{So how does this affect crowd work?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}
}

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
%   \nobalance{}
%   }
\endnotetext{
\section{Cases notes}
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,      particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
  % }
  % \endnotetext{
  \subsection{What forms of work design and worker management are viable?}
  \begin{itemize}
    \item researchers have looked at how to increase worker productivity
    (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
    \cite{measuringCrowdsourcingCheng}.
    \item we've also seen people ``embrace error''
    \cite{embracingErrorKrishna}.
    \item still other research has looked into ways to sandbox workers from the context of their work 
    \item but scholarship looking into the design and management of work and workers isn't new;
    lots of research into getting pieceworkers to do work more quickly
    \cite{seymour1954manual}.
    \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
    (echoing similar research on Wikipedia and Mechanical Turk)
    \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
  \end{itemize}

### 2016-12-05 drafts/labor/conclusion.tex
intro revisions
proposal (why didn't i put this up sooner?)

\begin{document}
\section{Conclusion}
Crowd work and on--demand work are not new: they are modern instantiations of piecework.
In this paper, we reconsider three major research questions in crowd work using the lens of piecework: \begin{inlinelist}
  \item ``\namerefl{sec:complexity}?'';
  \item ``\namerefl{sec:decomposition}?'';
        and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon. 
% predictions and to contextualize the answers that crowd work researchers have already uncovered.
% We subsequently take this historical framing to ask broader questions of crowd work, including among others what the future of crowd work holds for workers.
Reciprocally, we believe that modern crowd work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

>>>>

\begin{document}
\section{Conclusion}
Crowd work and on--demand work are not new: they are contemporary instantiations of piecework.
In this paper, we reconsider three major research questions in crowd work using the lens of piecework:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?'';
  \item ``\namerefl{sec:decomposition}?''; and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern crowd work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

### 2016-12-05 drafts/labor/decomposition.tex
proposal (why didn't i put this up sooner?)

\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work consist of creative methods for decomposing goals.} Even when tasks such as writing and editing cannot be reliably performed by individual workers, researchers demonstrated that decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,bernsteinSoylent,writingMicroTasks,Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows, which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g., a paragraph topic~\cite{crowdForgeKittur}, an error~\cite{bernsteinSoylent}, or a concept~\cite{Yu2016a,Yu2016b} and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas, including food labeling~\cite{noronha2011platemate}, brainstorming~\cite{siangliulue2015toward,yu2014distributed}, and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

\topic{If decomposition is key to success in crowd work, the question arises: what can, and can't, be decomposed?} 
Moreover, how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better, and the microtask paradigm has emerged as the overwhelming favorite~\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers, preventing a single errant submission from impacting the agenda of the work as a whole %, fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense, finer decompositions are seen as more robust --- both to interruptions and errors~\cite{cheng2015break} --- even if they incur a fixed time cost.
At the extreme, recent work has attempted demonstrated microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267} or even tenths of a second~\cite{embracingErrorKrishna}.
%Earlier we discussed \citeauthor{cheng2015break}'s work measuring the impact that interruption has on worker performance \cite{cheng2015break}.%While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components in the form of higher cumulative time to complete (albeit much shorter real time to complete, owing to parallelization)%
However, workers perform better when similar tasks are strung together ~\cite{delayAndOrderLasecki}, or chained and arranged to maximize  the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this, 
%rather than attempt to minimize the error rates in micro--tasks
%, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

% \topic{The crowdsourcing research into work decomposition
% has largely focused on minimizing the additional context necessary to do tasks%
% , and making it easier to do tasks with less time.}
% This first thread is
% perhaps best described by \citeauthor{verroios2014context} as
% making crowd workers ``\dots able to act with
% global understanding when each contributor only has access to local views''
% \cite{verroios2014context}.
% With the exception of a few cases
% (specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
% which finds that greater work context fosters more reliably high--quality work)%
% , the micro task paradigm has emerged as the overwhelming favorite
% \cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
% ,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes, the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.%
Workers seek out good requesters~\cite{martin2014being} and then  ``streak'' to perform many tasks of that same type~\cite{taskSearch}.
%, and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}), % does anyone care for project names?
%while other work designs tasks around gap time (\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning}) \cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,       Cai:2015:WLW:2702123.2702267}.

% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
Researchers have reacted by designing task recommendation systems (e.g.,~\cite{Cosley:2007:SUI:1216295.1216309})
%attempts to address this by directing workers to tasks through ``intelligent task routing'' \cite{Cosley:2007:SUI:1216295.1216309}.
and others focused on minimizing the amount of time that people need to spend doing anything other than the work for which they are paid~\cite{callison2014crowd}.

@@

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out, piecework most greatly benefits the instrumented measurement of workers, but certainly in Ford and Taylor's time, highly instrumented, automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result, the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.
\msb{This subsection is too shallow and needs a bit more. For example, can you give examples of the last point?}

@@

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled, edited, and redeployed~\cite{hu1961parallel}.
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code~\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago~\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

However, decomposition has hit a second bottleneck: cognition. 
Task switching costs and other cognitive costs make it difficult to work tasks so far decontextualized from their original intention \cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context, and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context --- for example, logo design requires a deep understanding of the client and their goals.
In part due to this limitation, 99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

>>>>

\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work
consist of creative methods for decomposing goals.}
Even when tasks such as writing and editing cannot be reliably performed by individual workers,
researchers demonstrated that
decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,
                                                               bernsteinSoylent,
                                                               writingMicroTasks,
                                                               Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows,
which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g.,
a paragraph topic~\cite{crowdForgeKittur},
an error~\cite{bernsteinSoylent},
or a concept~\cite{Yu2016a,Yu2016b} and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas,
including food labeling~\cite{noronha2011platemate},
brainstorming~\cite{siangliulue2015toward,yu2014distributed},
and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

\topic{If decomposition is key to success in crowd work,
the question arises: what can,
and can't,
be decomposed?} 
Moreover,
how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better,
and the microtask paradigm has emerged as the overwhelming favorite~\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work,
that microtasks should be designed resiliently against the variability of workers,
preventing a single errant submission from impacting the agenda of the work as a whole %,
fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense,
finer decompositions are seen as more robust
--- both to interruptions and errors~\cite{cheng2015break} ---
even if they incur a fixed time cost.
At the extreme,
recent work has attempted demonstrated
microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267}
or even fractions of a second~\cite{embracingErrorKrishna}.
However,
workers perform better when similar tasks are strung together~\cite{delayAndOrderLasecki},
or
chained and arranged to maximize the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this,
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

\topic{As the additional context necessary to complete a task diminishes,
the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.
Workers seek out good requesters~\cite{martin2014being} and then 
``streak'' to perform many tasks of that same type~\cite{taskSearch}.
and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}),

Researchers have reacted by designing task recommendation systems~\cite[e.g.][]{Cosley:2007:SUI:1216295.1216309}
and others focused on
minimizing the amount of time that people need to spend doing anything other than
the work for which they are paid~\cite{callison2014crowd}.

@@

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers,
but certainly in Ford and Taylor's time,
highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result,
the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

@@

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled,
edited,
and redeployed~\cite{hu1961parallel}.
In contrast,
today system--designers can share,
modify,
and instantiate environments
like sites of labor in a few lines of code~\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions,
and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago~\cite{dai2015and,
                                                              Cai:2016:CRI:2858036.2858237,
                                                              cheng2015break,
                                                              measuringCrowdsourcingCheng,
                                                              embracingErrorKrishna}.

@@

However,
decomposition has hit a second bottleneck: cognition. 
Task switching costs and other cognitive costs make it difficult
to work on tasks so far decontextualized from their original intention \cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context,
and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context
--- for example,
logo design requires a deep understanding of the client and their goals.
In part due to this limitation,
99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

### 2016-12-05 qual_management/main.tex
proposal (why didn't i put this up sooner?)

\documentclass[11pt]{article}
\usepackage{balance,graphics,setspace,parskip,times,hyperref,titling,microtype}
\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}
\usepackage[citestyle=numeric,backend=biber]{biblatex}
\bibliography{references}
\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\LARGE{\@title}}

  \@author
\end{flushleft}\egroup
}
\makeatother
\title{Externalizing Worker Qualifications}
\author{Ali Alkhatib}

\begin{document}
\maketitle{}

\section*{Background}
Labor market platforms ranging industries and styles of work
(e.g. Uber, TaskRabbit, UpWork, and Amazon Mechanical Turk)
have struggled for years with persistent and
in some cases growing
challenges relating to worker qualifications.
These issues range a wide spectrum:
in some cases, worker qualifications are non--transferable,
leading requesters to ``re--invent the wheel'' as they attempt to determine
in their own way whether a potential worker is qualified and reliable.

@@

% \textit{I want to communicate something along the lines of how
% these labor markets shouldn't be expected
% to handle these problems very well, because
% they've been focusing on sparking a form of commerce that hasn't existed before,
% etc\dots
% but I feel like this sounds too much like
% ``It's no wonder you all have failed!'' and
% I feel like there's no way to dig myself out of that hole.
% Thoughts?}

@@

This approach may prove useful in
alleviating the burden online labor markets are increasingly taking on.
By externalizing worker qualifications, a number of benefits can emerge:
\begin{enumerate}
  \item New workers can provide some evidence of their work history to labor platforms,
        mitigating or even resolving the ``cold start'' problem of
        not knowing the trustworthiness or competence of a new user.
  \item Aggregated (even heterogeneous)
        ratings sourced from differing labor markets can provide
        a more holistic picture of a worker's areas of competence.
        Workers can use this information to identify specialization more easily,
        reducing wasted time \textit{searching for} or \textit{working on} suboptimal tasks.
        Requesters can benefit from this information by
        making more informed decisions about which worker to contract.
  \item By turning the reputation management of workers into an external entity
        (agnostic to labor platform),
        designers and developers can focus more fully on the marketplace itself.
\end{enumerate}

@@

\section*{Measurable Variables}

\section*{First Steps}

>>>>

\documentclass[11pt]{article}
\usepackage{balance,graphics,setspace,parskip,fourier,hyperref,titling,microtype}
\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}
\usepackage[citestyle=numeric,backend=biber]{biblatex}
\bibliography{references}

\begin{document}
\section*{{\LARGE Externalizing Worker Qualifications}}
\section*{Background}
Labor market platforms ranging industries and styles of work
(e.g. Uber, TaskRabbit, UpWork, and Amazon Mechanical Turk)
have struggled for years with persistent
(generally growing)
challenges relating to worker qualifications.
These issues range a wide spectrum:
in some cases, worker qualifications are non--transferable,
leading requesters to ``re--invent the wheel'' as they attempt to determine
in their own way whether a potential worker is qualified and reliable.

@@

% \textbf{I want to communicate something along the lines of how
% these labor markets shouldn't be expected
% to handle these problems very well, because
% they've been focusing on sparking a form of commerce that hasn't existed before,
% etc\dots
% but I feel like this sounds too much like
% ``It's no wonder you all have failed!'' and
% I feel like there's no way to dig myself out of that hole.
% Thoughts?}

@@

This approach may prove useful in
alleviating the burden online labor markets are increasingly taking on.
By externalizing worker qualifications, a number of benefits can emerge:
\begin{enumerate}
  \item New workers can provide some evidence of their work history to labor platforms,
        mitigating or even resolving the ``cold start'' problem of
        not knowing the trustworthiness or competence of a new user.
  \item Aggregated (even heterogeneous)
        ratings sourced from differing labor markets can provide
        a more holistic picture of a worker's areas of competence.
        Workers can use this information to identify specialization more easily,
        reducing wasted time \textit{searching for} or \textit{working on} suboptimal tasks.
        Requesters can benefit from this information by
        making more informed decisions about which worker to contract.
  \item By turning the reputation management of workers into an external entity
        (agnostic to the labor platform),
        designers and developers can focus more fully on the marketplace itself.
\end{enumerate}

@@

\section*{Measurable Variables}
We see two measurable variables that might be relevant to
the goal of better, or higher--quality, crowd (and other on--demand) work.
The first, accuracy of predicting worker acceptance rates, is fairly straightforward.
The second, determining whether workers better self--evaluate in their selection of work
based on more comprehensive awareness of their reputation (or credibility).
We'll call this latter dimension ``worker self--specialization'' to allude to
the emergent property of workers identifying their own niche expertises and
selecting for tasks in those domains.

\subsection*{Worker Accuracy}
Determining a worker's likelihood of completing a task correctly is
fundamentally the goal of using past worker approval rates
(like on AMT, Upwork, and other platforms)
as a low pass filter for workers.
The thinking goes that past performance is an indicator towards future performance.

The baseline approaches requesters have used typically falls into two paths:
\begin{enumerate*}
  \item Relying principally on the platform's rating system as a broad--spectrum filter, and
  \item Implementing one's own rating or qualification system as a determiner of
        whether or not to allow someone to do tasks of similar nature.
\end{enumerate*}

We can conduct post--facto analyses of workers' data
(aggregated from their various work platforms) to see
if any combination and/or weighting of their
worker profiles from multiple platforms
more accurately predicts their likelihood of doing good work than the ``baseline''
(that is, informed solely by the platform on which the work was solicited).

To run this analysis, we would need to solicit new information from workers
than they've traditionally shared.
Specifically,
workers would need to be willing to share approval rates from other work platforms
(such as AMT or CrowdFlower).

\subsection*{Worker Self--Specialization}
The next dimension that we could evaluate would be
to use this data to better--inform workers about their approval trends.
The best way to run this experiment would be
to randomly assign some number of workers to a control group and
some others to an experimental group, wherein these workers have the opportunity
(after sharing their aggregated profiles with us)
to see at a higher level on what \textit{types} of work they typically fare better.

The operationalization of this dimension would almost certainly be
the measurement of overall approval rates over time after intervention.
To make this more concrete, we would provide workers with guidance on what
sorts of work they typically get approved, perhaps
helping to guide them to those kinds of work more actively than otherwise.

There are problems with the experimental design described at the outset.
For one thing, finding willing participants might be difficult, and
randomly sampling for potential participants would make
recruitment of a sufficiently large cohort difficult.
Moreover, the self--selection of workers into this group
(or rather, out)
would almost certainly compromise the ``randomness'' of the assignment approach.

Instead, it may be better simply to allow
a limited number of interested participants
to sign up to participate in a ``pilot program'',
incorporating their work data from other platforms.
While it's true that this would otherwise be ``giving up'' on randomized experimentation,
the question of
what types of workers would prefer this sort of work is
its own important area of discussion that we shouldn't try to evade.

\section*{First Steps}
The first step is to solicit workers
(either on AMT, Upwork, or another platform)
who may be interested in participating in a study of this nature.
We'll ask these participants to self--report their own approval rates from each platform,
perhaps asking for an annotated history of their tasks
(if feasible).

Two methods of evaluation may be viable, depending on the homogeneity of the tasks.
One approach would be
to train a machine learning model on a subset of the aggregated data
and test it against other subset of that data.

The other approach would be
to investigate the nature of the tasks that are being done,
categorize them by similarity, and
focus on trying to predict worker quality from the aggregated approval rates across platforms
(for instance, looking at the worker's approval rates for translations across AMT and Upwork).

% During this time, or perhaps later,
% we would run workers through a number of tasks.
% At first, an \textit{a priori} estimate of
% their likelihood to return a correct response would be unnecessary,
% as we would initially be exploring the data for indicators
% across the aggregated data
% that may be predictive.

% We could either use a training--test approach
% (a fairly straightforward approach in machine learning ---
% to train on a portion of the dataset and
% test on another (specifically, one that the learning algorithm has never seen)).

A later step is
to build a prototypical server serving the basic needs of
an aggregated reputation service.
That is,
if a client queries the service for information about a worker on Upwork,
the client will receive a reasonably comprehensive snapshot of the worker's
history on other platforms.
